A Deterministic and Terminating Semantics for the Synchronous Programming Language~\CEU

### 2018-02-02 index.tex
Abstract reescrito. Tirei a frase com "some equivalence results". Guilherme, que equivalências são essas?

\begin{abstract}
\CEU is a synchronous programming language for embedded soft real-time systems.
%
It supports advanced features, such as safe shared-memory concurrency and
abortion of execution lines, while enforcing internal determinism and
time-bounded reactions.
%
In this paper, we present a small-step structural operational semantics for
\CEU and prove that under it program reactions are deterministic and always
terminate.
%
Thus, given the same timeline of input events, the same \CEU program in the
same initial memory state will always react in bounded time and arrive at the
same final memory state.
%
We also discuss some equivalence results and the relation between the proposed
semantics and its actual implementation.
\end{abstract}

>>>>

\begin{abstract}
\CEU is a synchronous programming language for embedded soft real-time systems.
%
It focus on control-flow safety features, such as safe shared-memory
concurrency and safe abortion of lines of execution, while enforcing internal
determinism and time-bounded reactions to the environment.
%
In this work, we present a small-step structural operational semantics for
\CEU and a proof that reactions are deterministic and always terminate:
%
For a given timeline of input events, multiple executions of the same program
always react in bounded time and arrive at the same final memory state.
%
%We also discuss some equivalence results and the relation between the proposed
%semantics and its actual implementation.
\end{abstract}
